%-% xelatex
%-\documentclass{article}
%-
%-\usepackage[utf8]{inputenc}
%-
%-\usepackage{ot-tableau}
%-\usepackage[backend=biber, style=authoryear-icomp]{biblatex}
%-\usepackage{easylist}
%-\usepackage{hanging}
%-\usepackage{hyperref}
%-\usepackage{blindtext}
%-\usepackage{tipa}
%-\usepackage{cgloss4e}
%-\usepackage{gb4e}
%-\usepackage{qtree}
%-\usepackage{enumerate}
%-\usepackage{multicol}
%-\addbibresource{$HOME/doc/cit/uni.bib}
%-
%-\title{The road studie guide}
%-\author{Preston Precourt}
%-
%-\begin{document}
%-
%-\maketitle
\index{the road}

\begin{multicols}{3}
  \begin{enumerate}
    \subsubsection{(1-7)}

    \item Where is the man and the boy going? Why?
    
    They’re going to the ocean for water.
    
    \item Think about the literary style of the book why is this different than normal books
    
    Because it’s not as good as normal books.

    \item Explain the quote “I suppose this book is a love story to my son”:

    He cares about his son.
    
    \subsubsection{(8-17)}
    
    \item what does the father mean when he says, “you forget what you want to remember and remember what you want to forget?”

    He means what he said.

    \item Why new vocab?

    New words for new world.

    \item Concerns?

    Food and shoes.

    \subsubsection{(18-33)}

    \item Good dreams?

    Because they help you sleep

    \item “treat”?

    Soda.

    \item  Danger?

    There could be someone living there.

    \item Referring?

    Can he kill himself if he is in danger?

    \item That boy?

    He will probably kill himself if the boy dies

    \subsubsection{(34-48)}

    \item promised?

    Think about the boy all the time.

    \item waterfall?

    I think it was dumb to go in the water it could be contaminated.

    \item old?

    7 years

    \item cart?

    Bad idea.

    \item Truck?

    There were dead bodies, human trafficking.

    \subsubsection{(49-60)}

    \item What do they do?

    They follow him.

    \item Boy wants to?

    Help him

    \item Wallet?

    He is over his wife

    \item Hope?

    To keep him from being like his mother.

    \item Names?

    They aren’t important to the story.

    \item Argument?

    The wife wants to die but he doesn’t.

    \item goodbye?

    Not change her mind.

    \subsubsection{(60-79)}

    \item Realistic?

    No how would the fuel work

    \item Animals, tattoo?

    No animals.

    \item Doc?

    Probably because he knew stuff.

    \item What happened?

    He was shot by the man.

    \item Fathers job?

    Keeping his son safe.

    \subsubsection{(78-89)}

    \item Kill the dog?

    Its un necessary

    \item Meaning “fire”?

    Were safe because we have fire.

    \item Real?

    No, it’s not real.

    \subsubsection{(90-105)}

    \item Orchard?

    Footprints. It just snowed.

    \item Armed

    There part of the army helping people.

    \item Move?

    There is something bad coming.

    \item Strat?

    Hide and watch.

    \subsubsection{(105-113)}

    \item Suspense use?

    He uses suspense to confuse the reader.

    \item Help?

    He could get caught.

    \item Saw but not?

    He felt stupid because he didn’t realize that he was in a bad place.

    \subsubsection{(114-130)}

    \item Escape?

    The run.

    \item House?

    He finds car fuel.

    \item Why is the man concerned?

    He could be dying

    \item Reaction?

    He wants to help them.

    \subsubsection{(131-144)}

    \item wish

    he is lonely.

    \item How does he know?

    The buildings are empty of goods.

    \item God guys?

    They don’t kill people. To teach the kid to be a good guy too.

    \item find?

    A vault, they are dead.

    \item Real?

    Not very likely

    \subsubsection{(145-156)}

    \item Before eating?

    He thanks the people who died.

    \item Disaster.

    A bomb.

    \item One?

    The kid can’t carry one

    \item Why don’t they stay?

    They hear a dog.

    \subsubsection{(157-167)}

    \item Sun?

    ash clouds.

    \item Reason

    It’s raining.

    \item Old?

    No, he is lying a lot.

    \subsubsection{(168-180)}

    \item Explain “beggars”?

    Need is different from want.

    \item Why Food?

    The boy\index{the boy} is kind.

    \subsubsection{(180-195)}

    \item Foreshadowing?

    The dad might die.

    \item Pharmacy?

    it has no use.

    \item Distance?

    The bad dream

    \item Watching eat?

    He’s hungry

    \item Followed?

    There always being followed.

    \subsubsection{(196-204)}

    \item Trees?

    The end of the world
    
    \item Shoot the gun?

    Nothing

    \item cooking?

    They were in a rush.

    \item Emotional

    He isn’t as disturbed.

    \item Baby … from where?

    The pregnant lady with them

    \item Father feels?

    Bad.

    \subsubsection{(205-213)}

    \item Decision?

    He is dying.

    \item Find?

    Nothing, this is a bad book

    \subsubsection{(213-223)}

    \item Look?

    He’s never seen a deer.

    \item Find?

    Nothing

    \item Play?

    He’s dumb

    \item check the boat

    check for food

    \subsubsection{(223-240)}

    \item what does he find on the boat

    nothing

    \item keep going?

    the son

    \item mad?

    the father is nice.

    \item Problem?

    It wasn’t

    \item Camp?

    He walks.

    \item Flare uses?

    To catch someone on fire.

    \subsubsection{(240-253)}

    \item Good idea?

    No, they could be caught

    \item Scarred?

    The boy\index{the boy} might die

    \item When they find him?

    They will steal his clothes.

    \subsubsection{(253-270)}

    \item Find him?

    They look for snow.
  \end{enumerate}
\end{multicols}
%-\end{document}
