
\documentclass[12pt]{article}

%
%Margin - 1 inch on all sides
%
\usepackage[margin=1in]{geometry}
\usepackage{times}

%
%Doublespacing
%
\usepackage{setspace}
\doublespacing

%
%Fancy-header package to modify header/page numbering (insert last name)
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{Precourt \thepage}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%To make sure we actually have header 0.5in away from top edge
%12pt is one-sixth of an inch. Subtract this from 0.5in to get headsep value
\setlength\headsep{0.333in}



%
%Begin document
%
\begin{document}
\begin{flushleft}

%%%%First page name, class, etc
Preston Precourt\\
Ganter\\
Ela 10\\
2018-9-20\\
\end{flushleft}

%%%%Title
\begin{center}
Why we are bad
\end{center}


%%%%Changes paragraph indentation to 0.5in
\setlength{\parindent}{0.5in}
%%%%Begin body of paper here

Humans are detrimental to the planet. This is because we are eating too much meat and creating too much greenhouse gasses and changing global climate.  

We eat too much meat does not mean that we need to give up meat entirely but if we give up meat for even one day a week (Discovery Communications) we can help lower demand for meat therefore, create less supply and less supply means less animals. 5/6 of greenhouse gas production is made by cows, so if we skip meat eating 1/7 of the week then we get rid 7/42 of the worlds current methane production. And less methane means less greenhouse gasses also less meat consumption means less cows resulting in the second worse planetary boundary “Generic Diversity” (text2, Graphic).  

Greenhouse gasses are the primary cause of global warming (A form of global climate change). If global warming were make “earth to move to a warmer state, 5 to 6 degrees [ degrees Celsius ] warmer, with no ice caps, it will do so and that won’t be good for large mammals like us.”(Text2, lines 46-47) this isn’t good for us because we will most likely have  this occur if we don’t  do anything, and we don’t seem to be doing anything. 

Global climate is also changing because of us, even though you may say that it isn’t changing because your ac unit is creating cold air the energy used to make that air cold creates warm air. We’re killing animals 50\% faster because of co2, pollution, and mass fishing. (Discovery Communications) global climate change is probably one of the most relevant enduring issues 

One may say our technology can save the world from us, but the quote “Technologies from before I was born are basically invisible to me. It scarcely matters how powerful and dangerous they are.” (Text 3, Line) counters this because if you are born after a power plant was regularly used you don’t see how much it changes the environment every time you turn it on. 

\end{document}

